A Fully Decentralized Infrastructure for Automated and Trusted IoT Data Trading

### 2020-06-01 paper.tex
Minor tweaks

\section{System Design Thinking}
\subsection{The Architecture}
% TODO: pub/sub model selection
% use IPFS as searching indexes
\subsection{Choice of Data Storage}
Data storage is an important element of data marketplace where the data assets are reserved. We assume such storage system should be distributed which runs on the peer-to-peer network maintiaining by multiple nodes. Hence, the risk of system paralysis for server being compromised or shutdown unexpectedly can be removed. Among the existing distributed storage mentioned in Section~\ref{section:relatedWork}, different architectures, back-up mechanisms and access controls strategies are proposed. Yet the keys and addresses of data managed by participants are hard to be as small as possible especially for data streams.

@@

\section{Decentralized Data Marketplace Case Study}
\subsection{Participants in Decentralized Data Marketplace}
There are three major roles, data providers, data consumers and brokers in the decentralized data marketplace which is similar to the pub/sub messaging model. But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others. In our proposed architecture, the brokers are only responsible for message delivery and essential verification processes. Fig.~\ref{fig:system_design}

\subsection{Trading Models of Decentralized Data Marketplace}
\subsubsection{Set Up}
All participants need to register on TangleID\cite{TangleID}, a self-soverign identity system built on top of MAM, enables authentication without any third party via a decentralized identifiers and a public/private key pair for authentication.

>>>>

\section{System Design Thinking}
\subsection{The Architecture}
% TODO: pub/sub model selection
There are three major roles, data providers, data consumers and brokers in the decentralized data marketplace which is similar to the pub/sub messaging model. But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others. In our proposed architecture, the brokers are only responsible for message delivery and essential verification processes. Fig.~\ref{fig:system_design}

% use IPFS as searching indexes
\subsection{Choice of Data Storage}
Data storage is an important element of data marketplace where the data assets are reserved. We assume such storage system should be distributed which runs on the peer-to-peer network maintiaining by multiple nodes. Hence, the risk of system paralysis for server being compromised or shutdown unexpectedly can be removed. Among the existing distributed storage mentioned in Section~\ref{section:relatedWork}, different architectures, back-up mechanisms and access controls strategies are proposed. Yet the keys and addresses of data managed by participants are hard to be as small as possible especially for data streams.

@@

\section{Decentralized Data Marketplace Case Study}
Trading Models of Decentralized Data Marketplace
\subsubsection{Set Up}
All participants need to register on TangleID\cite{TangleID}, a self-soverign identity system built on top of MAM, enables authentication without any third party via a decentralized identifiers and a public/private key pair for authentication.
